Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits

### 2022-09-14 04_paper/0913_draft.Rmd
figures + descriptions
Also I change the way to referencing figures

---
title: "Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits"
author: ["Lucie Lu","Miles D. Williams"]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    number_sections: yes
classoption: fleqn
fontfamily: mathpazo
fontsize: 12pt
bibliography: ref_xinhua.bib
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \setlength{\mathindent}{15pt}
  - \setlength\parindent{24pt}
  - \setlength{\parskip}{0.0pt plus 1.0pt}
  - \doublespacing
  - \newtheorem{theorem}{Theorem}[section]
  - \newtheorem{lemma}[theorem]{Lemma}
  - \newtheorem{proposition}[theorem]{Proposition}
  - \newtheorem{corollary}[theorem]{Corollary}
  - \newenvironment{proof}[1][Proof]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries Proof}]}{\end{trivlist}}
  - \newenvironment{definition}[1][Definition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{example}[1][Example]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{remark}[1][Remark]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{!t}
  - \usepackage{caption}\captionsetup[table]{skip=5pt}
  - \usepackage{dcolumn}
  - \usepackage{rotating}
  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}

@@

Figure 1 shows total ODA (aid) and OOF (debt) disbursed by Beijing per year from 2002 to 2017. Values are shown in millions of 2017 USD. Blue shows values for aid and red shows values for debt. The difference in China's application of debt relative to aid is stark, and the gulf only expands over time.

This explosion in debt relative to aid aligns with a shift in Beijing's strategy going into the twenty-first century. Burdened with vast foreign currency reserves due to years-long trade surpluses, confronted with excess domestic production of industrial goods, and in need of access to resources to support its continued economic growth, Beijing tasked its so-called policy banks to help Chinese firms gain access to foreign markets [@dreher_banking_2022]. This focus spurred a radical change in China's development finance portfolio. As @dreher_banking_2022 put it, "Beijing began to behave less like a benefactor and more like a banker" (5). Figure 1 shows this transformation from donor to lender in the starkest of terms.

```{r, fig.cap='Total yearly ODA (aid) and OOF (debt) issued by China from 2002 to 2017 in millions of 2017 constant USD.'}
library(knitr)
library(here)
include_graphics(
  here('06_figures/aid_debt_trends.png')
)
```

```{r, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.'}
include_graphics(
  here('06_figures/dev_countries_over_time_by_type.png')
)
```

Not only has the composition of China's total international development financing changed over time, so has its portfolio of developing countries. Figure 2 shows yearly trends in the number of developing countries in the data sample by whether they exclusively receive Chinese aid (blue), exclusively are Chinese debtors (red), are both (green), or are neither (grey). The most substantial change over time has been in the number of developing countries that are neither recipients nor debtors with respect to Chinese development financing. In 2002 more than 70 of the developing countries in the sample were neither recipients nor debtors of Beijing's. By 2017 the count declined to 24.

@@

@@

```{r, fig.cap='Number of \\textit{Xinhua} mentions and diplomatic missions from Beijing per year by developing country aid-recipient status (top) and debtor status (bottom).', out.width="100%",fig.show='hold'}
include_graphics(
  c(here('06_figures/rate_coverage_visits_by_aid.png'),
    here('06_figures/rate_coverage_visits_by_debt.png'))
)
```

Figure 3 shows trends in the number yearly *Xinhua* mentions of developing countries in the sample and the number of yearly diplomatic visits these countries host. The left frame of each panel shows the mean number of *Xinhua* mentions per developing country per year, and the right frame of each panel shows the mean number of diplomatic visits per developing country per year. In the top, the sample is divided by status as a Chinese aid recipient. Blue denotes the trend in yearly mentions in *Xinhua* and diplomatic visits per country among recipients of Chinese aid, whereas red denotes these trends among non-recipients. In the bottom panel, the sample is divided by status as a Chinese debtor. Blue denotes the same trends in the top panel, but in this case for Chinese debtors. Meanwhile, red denotes these trends among non-debtors.

@@

```{r, fig.cap='Estimated Negative Binomial model coefficients with 95\\% confidence intervals. Controls and year fixed effects not shown. Models were estimated with random recipient intercepts.'}
include_graphics(
  here('06_figures/neg_binom_estimates.png')
)
```

```{r, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.'}
include_graphics(
  here('06_figures/predicted_differences.png')
)
```

>>>>

---
title: "Friends Get More Money, Attention and Handshakes: Chinese Foreign Aid, Xinhua and Diplomatic Visits"
author: ["Lucie Lu","Miles D. Williams"]
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::pdf_document2: 
    toc: false
classoption: fleqn
fontfamily: mathpazo
fontsize: 12pt
bibliography: ref_xinhua.bib
link-citations: yes
linkcolor: blue
header-includes:
  - \usepackage{amsmath}
  - \usepackage{setspace}
  - \setlength{\mathindent}{15pt}
  - \setlength\parindent{24pt}
  - \setlength{\parskip}{0.0pt plus 1.0pt}
  - \doublespacing
  - \newtheorem{theorem}{Theorem}[section]
  - \newtheorem{lemma}[theorem]{Lemma}
  - \newtheorem{proposition}[theorem]{Proposition}
  - \newtheorem{corollary}[theorem]{Corollary}
  - \newenvironment{proof}[1][Proof]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries Proof}]}{\end{trivlist}}
  - \newenvironment{definition}[1][Definition]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{example}[1][Example]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newenvironment{remark}[1][Remark]{\begin{trivlist}
      \item[\hskip \labelsep {\bfseries 1}]}{\end{trivlist}}
  - \newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.5em depth0.25em\fi}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \floatplacement{figure}{!t}
  - \usepackage{caption}\captionsetup[table]{skip=5pt}
  - \usepackage{dcolumn}
  - \usepackage{rotating}
  - \usepackage{caption}\DeclareCaptionLabelFormat{AppendixTables}{A.#2}

@@

Figure \@ref(fig:total-aid-debt) shows total ODA (aid) and OOF (debt) disbursed by Beijing per year from 2002 to 2017. Values are shown in millions of 2017 USD. Blue shows values for aid and red shows values for debt. The difference in China's application of debt relative to aid is stark, and the gulf only expands over time.

This explosion in debt relative to aid aligns with a shift in Beijing's strategy going into the twenty-first century. Burdened with vast foreign currency reserves due to years-long trade surpluses, confronted with excess domestic production of industrial goods, and in need of access to resources to support its continued economic growth, Beijing tasked its so-called policy banks to help Chinese firms gain access to foreign markets [@dreher_banking_2022]. This focus spurred a radical change in China's development finance portfolio. As @dreher_banking_2022 put it, "Beijing began to behave less like a benefactor and more like a banker" (5). Figure \@ref(fig:total-aid-debt) shows this transformation from donor to lender in the starkest of terms.

```{r total-aid-debt, fig.cap='Total yearly ODA (aid) and OOF (debt) issued by China from 2002 to 2017 in millions of 2017 constant USD.'}
library(knitr)
library(here)
include_graphics(
  here('06_figures/aid_debt_trends.png')
)
```

```{r 4-types, fig.cap='Number of developing countries per year that are (a) beneficiaries of Chinese aid, (b) debtors, (c) both, and (d) neither.'}
include_graphics(
  here('06_figures/dev_countries_over_time_by_type.png')
)
```

Not only has the composition of China's total international development financing changed over time, so has its portfolio of developing countries. Figure \@ref(fig:4-types) shows yearly trends in the number of developing countries in the data sample by whether they exclusively receive Chinese aid (blue), exclusively are Chinese debtors (red), are both (green), or are neither (grey). The most substantial change over time has been in the number of developing countries that are neither recipients nor debtors with respect to Chinese development financing. In 2002 more than 70 of the developing countries in the sample were neither recipients nor debtors of Beijing's. By 2017 the count declined to 24.

@@

```{r aid-debt-country, fig.cap='Top 20 Chinese Aid Recipients (left) and Debt Recipients (right) on Average from 2002 to 2017.', out.width="100%",fig.show='hold'}
include_graphics(
  here('06_figures/aid_debt.jpg'))

```

Figure \@ref(fig:aid-debt-country) shows the top-20 Chinese aid and debts recipient countries on average between 2002 and 2017. Notably, on average, Iraq received 500 million in aid but borrows 0 dollars of loan from China. In contrast, Russia borrowed almost 8,000 million dollars from China but received no aid at all. There is little overlap between the top recipient countries that receive both aid and debt from China. There are stark variations in terms of the amounts China lends. Russia and Venezuela were the only countries that borrowed more than 5,000 million dollars debt on average, the sum of which accounted for about 30% of the total lending amounts of the top-20 debt recipients. Eight countries are shown on both the left and right frames: Indonesia, Pakistan, Laos, Ethiopia, Cambodia, Sri Lanka, Kenya, and Sudan. Geographically, five are in South or East Asia, whereas three are in Africa.

In terms of the compositions of debt and aid for the top 20 beneficiaries of total amount of both aid and debt, Figure \@ref(fig:compositions) shows that 14 out of 20 countries received over 80% of debt in their portfolio. The top 5 recipients, Russia, Venezuela, Angola, Kazakhstan and Brazil received support from China almost purely in the form of loans. Kazakhstan is the only exception among the five beneficiaries that received slightly 2\% of aid in its portfolio. We can infer that Beijing invests more heavily in its debt, comparing to its aid distribution. In consistent with the trends demonstrated in Figure \@ref(fig:4-types), China takes a targeted approach with debt.

```{r compositions, fig.cap='The Aid-Debt Composition of the Top 20 Chinese Aid and Debt Recipients on Average from 2002 to 2017.', out.width="100%",fig.show='hold'}
include_graphics(
  here('06_figures/portfolio.jpg'))

```

@@

```{r aid-debt-cov, fig.cap='Number of \\textit{Xinhua} mentions and diplomatic missions from Beijing per year by developing country aid-recipient status (top) and debtor status (bottom).', out.width="100%",fig.show='hold'}
include_graphics(
  c(here('06_figures/rate_coverage_visits_by_aid.png'),
    here('06_figures/rate_coverage_visits_by_debt.png'))
)
```

Figure \@ref(fig:aid-debt-cov) shows trends in the number yearly *Xinhua* mentions of developing countries in the sample and the number of yearly diplomatic visits these countries host. The left frame of each panel shows the mean number of *Xinhua* mentions per developing country per year, and the right frame of each panel shows the mean number of diplomatic visits per developing country per year. In the top, the sample is divided by status as a Chinese aid recipient. Blue denotes the trend in yearly mentions in *Xinhua* and diplomatic visits per country among recipients of Chinese aid, whereas red denotes these trends among non-recipients. In the bottom panel, the sample is divided by status as a Chinese debtor. Blue denotes the same trends in the top panel, but in this case for Chinese debtors. Meanwhile, red denotes these trends among non-debtors.

@@

```{r binom-est, fig.cap='Estimated Negative Binomial model coefficients with 95\\% confidence intervals. Controls and year fixed effects not shown. Models were estimated with random recipient intercepts.'}
include_graphics(
  here('06_figures/neg_binom_estimates.png')
)
```

```{r predicted-diff, fig.cap='Counterfactual estimates of yearly \\textit{Xinhua} mentions and diplomatic missions from Beijing.'}
include_graphics(
  here('06_figures/predicted_differences.png')
)
```
